### 2016-05-26 syntax.tex
hammering on syntax

\heading{Hash-based (Bloom) filters.}
Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a triple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry})$.   
%
The randomized \emph{hash-sampling} algorithm~$\mathsc{H}$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m-1\})$.  We write $\mathcal{H} \getsr \mathsc{H}$ for this operation.
%
The deterministic representation algorithm $\mathsc{Rep}\colon [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.  (Recall that $[U]^n$ denotes subsets of~$U$ of size~$n$.)
%
The determinisitc query algorithm $\mathsc{Qry}\colon \Sigma^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  
%
We assume that both $\mathsc{Rep}$ and $\mathsc{Qry}$ have the following blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.   Thus, we write $M \gets \mathsc{Rep}^{\mathcal{H}}(S)$ and $b \gets \mathsc{Qry}^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.

For correctness, we demand that for all $\mathcal{H}$ and~$S$, and for all $x \in S, \mathsc{Qry}^{\mathcal{H}}(\mathsc{Rep}^{\mathcal{H}}(S),x)=1$.

\heading{Discusssion.}
This syntax captures classical Bloom filters by setting~$\Sigma=\bits$ and defining $\mathsc{Rep},\mathsc{Qry}$ in the obvious way.  Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location. \tsnote{Would let us capture a construction from NY, among other things.}

>>>>

\heading{Hash-based (Bloom) filters.}
Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a triple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry})$.   
%
The randomized \emph{hash-sampling} algorithm~$\mathsc{H}$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m-1\})$.  We write $\mathcal{H} \getsr \mathsc{H}$ for this operation.
%
The deterministic representation algorithm $\mathsc{Rep}\colon [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.  (Recall that $[U]^n$ denotes subsets of~$U$ of size~$n$.)
%
The determinisitc query algorithm $\mathsc{Qry}\colon \Sigma^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  
%
We assume that both $\mathsc{Rep}$ and $\mathsc{Qry}$ have the following blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.   Thus, we write $M \gets \mathsc{Rep}^{\mathcal{H}}(S)$ and $b \gets \mathsc{Qry}^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
%
For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\mathsc{Qry}^{\mathcal{H}}(\mathsc{Rep}^{\mathcal{H}}(S),x)=1}$, where the probability is over the sampling $\mathcal{H}\getsr\mathsc{H}$.

\heading{Discusssion.}
This syntax captures classical Bloom filters by setting~$\Sigma=\bits$ and defining $\mathsc{Rep},\mathsc{Qry}$ in the obvious way.  Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location. \tsnote{Would let us capture a construction from NY, among other things.}  We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\mathsc{Qry}$ returns a bit does not capture functionality of Bloom filters that employ counters, e.g., returning a counter value.

Our syntax also does not capture filters that are allowed to grow over time (e.g. ``scalable Bloom filters'') or cdertain kinds of hierarchical Bloom filters.  We turn our attention to this next.
